Extending Camellia for Distributed Stiffness Matrix Determination in DPG

### 2011-12-09 docs/HPC_report/Extending_Camellia.tex
added hp mesh partitioning to further
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@107 36274a68-8941-4c93-80ef-affaed5139da

\subsection{$hp$-meshes}
\subsection{Parallel solvers}
\subsubsection{MUMPS}

>>>>

\subsection{$hp$-meshes}

The Zoltan partitioner supports a weighted partitioning of a set of objects.  At the moment, every element is treated with equal weight, under the assumption that each contributes an equal number of degrees of freedom.  We would like to extend the partitioning to $hp$-adaptive meshes (where the polynomial order $p$ is allowed to vary element by element) by weighting each element by the number of internal degrees of freedom that it holds.

\subsection{Parallel solvers}
\subsubsection{MUMPS}
